 Total Team Spending and Profitability Results in a Higher League Ranking in the English Premier League

### 2024-04-19 paper/paper.qmd
Committing all changes made 04-19-2024 @3:05am.

# Display actual vs predicted points sorted by actual points descending
result_table <- analysis_data |> 
  select(team, pts, predicted_pts) |>
  arrange(desc(pts))

# Format table with LaTeX and apply additional styling
kable(result_table, booktabs = TRUE, align = c("l", rep("r", 6)), "latex", longtable = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)
```

>>>>

# Selecting the necessary columns and renaming them
result_table <- analysis_data |> 
  select(team, pts, predicted_pts) |>
  rename(Team = team, Points = pts, `Predicted Points` = predicted_pts) |>
  arrange(desc(Points))

# Round predicted points to the nearest whole number
result_table$`Predicted Points` <- round(result_table$`Predicted Points`, 0)

# Format table with LaTeX and apply additional styling
kable(result_table, booktabs = TRUE, align = c("l", "r", "r"), "latex", longtable = TRUE) |>
  kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10)
```
